Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-05 ms.tex
filled in caption for DIRBE correlation slope figure

\begin{figure*}
\begin{center}
\epsfig{file=dirbe_slopes.eps, width=6.5in}
\caption{\label{fig:dirbe_slopes} DIRBE linear fits for correlation slope 
analysis.}
\end{center}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\epsfig{file=dirbe_slopes.eps, width=6.5in}
\caption{\label{fig:dirbe_slopes} Linear fits of DIRBE 240$\mu$m (left), 
140$\mu$m (center), and 100$\mu$m (right) as a function of \PLANCK~857 GHz. The
red lines illustrate the DIRBE correlation slopes used in our global parameter 
analysis of $\S$\ref{sec:global}.}
\end{center}
\end{figure*}
